Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
...

	Our deviation model is drawn from \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}.

@@

	$P_+ = \psi (1 - d) + (1 - \psi) d$

@@

	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

	\newpage
	%$\,$
	%\newpage
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

>>>>

	Our deviation model is the same as \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}, that is random binary noise on edges.

	%gamma = infini meilleur sur une itération

@@

	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$.

@@

	%P(\mbox{no other vertex activated in any cluster})
	\begin{align*}
	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
	\end{align*}
	\newpage
	%$\,$
	%\newpage
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}
